%!TEX root = ../../master.tex
\section{Microservices, Thönes, 2015}

\begin{itemize}
  \item \textbf{What is a microservice?} In my mind, it is a small application that can be deployed independently, scaled independently, and tested independently and that has a single responsibility.
  \item \textbf{What would such a single thing be?} A single thing might be a single responsibility in terms of a functional requirement, or it might be in terms of nonfunctional requirement or, cross-functional requirements.
  \item \textbf{Why has microservices become popular?} Applications have been growing for 2, 5, or maybe 10 years, and it becomes hard to maintain them. Its difficult to make any functional changes. Companies realize that the need an approach that allows them to scale along different axes
  \item Microservices dont rely on being a particular language or particular back-end data store for your entire product stack, you get the flexibility to make informed decisions based on the right tooling for the situation at hand.
  \item \textbf{Why Event Service Busses are bad} They make your diagrams look nice. You look at your enterprise architecture and they've got all these crossing ugly lines. It's really tempting to put the ESB box in the middle because suddenly all your lines are straight. That's a great thing if you are an architect.
  \item But of course all the lines are still there. They're just in the middle of a spaghetti box. It still looks like a spaghetti bus.
  \item Microservices is the coming together of a bunch of better practices from a number of different communities. It is a combination of great stuff from the domain-driven-design community around strategic design, bounded context, subdomains, how to separate out your domains, and how to partition a very big problem domain into smaller domains so that you can manage them.
\end{itemize}
